    \begin{subsection}{Properties, Examples and Obstructions}
        
    Risk measures are now a standard tool for evaluation in actuarial science as well as in financial mathematics as a whole. 
    One of the most basic risk measures,
    \[ 
        \rho(X) = \mathbb{E}[X] 
    \] 
    dates back as early as 1709 to Nicolaus I Bernoulli’s PhD. thesis \cite{bernoulli1709dissertatio}, in which he proposed it as the fair price for insurance contracts.
    % https://pmc.ncbi.nlm.nih.gov/articles/PMC11928225/
    % Roman Law on the Just Price in Nicolaus Bernoulli’s Mathematics
    Remarkably, only a few years later, Bernoulli also suggested an adjustment based on individual preferences—a concept we would now recognize as a precursor to utility theory.
    It took several centuries, however, until Markowitz’s portfolio theory \cite{markowitzportfolio}, which introduced variance as a measure of risk, reignited the theory and 
    led to the early development of downside risk measures such as lower partial moments. Specifically, in 1959, Markowitz (Chapter 9 \cite{markowitzsemivariance}) proposed
    \[
        \mathbb{E}[(|\mathbb{E}[X] - X|\mathbf{1}_{ \{\mathbb{E}[X] - X > 0 \} })^k] 
    \] 
    Over the following decades, various risk measures flourished, mostly under the term "premium principle", 
    % A General Class of Three-Parameter Risk Measures Bernell K. Stone
    of which special mentioning deserves the value-at-risk 
    \[ 
        \rho(X) = \text{VaR}_{\lambda}(X) = \inf \{ m \in \mathbb{R} | \pp{X + m < 0} \leq \lambda \}
    \]
    and the expected shortfall, or average value at risk ,
    \[
        \rho(X) = \text{AVR}_{\lambda}(X) = \frac{1}{\lambda} \int_{0}^\lambda \text{VaR}_{\alpha}(X) d\alpha
    \]
    until in 2011 Föllmer and Schied \cite{foellmerschied} put the theory on rigorous axiomatic foundations.
    % Risk Measures and Theories of Choice Tsanakas
    While an algebraic approach to portfolio theory is already well developed—since it is inherently an optimization problem on an intersection of hyperplanes and a conic—
    the algebraic aspect of risk measures still offers ample room for development, to the best of the author’s knowledge. 
    \newline

    We first give some basic definitions for risk measures.
    Let \( \mathcal{X} = \mathcal{L}^p(\Omega, \mathcal{F}, \mathbb{P}) \) or subspace thereof, 
    for some suitable choice of \( p \).
    \begin{definition} \label{defriskmeasure}
    A mapping \( \rho : \mathcal{X} \to \mathbb{R} \) is called a monetary risk measure if it satisfies
    the following conditions for all \( X, Y \in \mathcal{X} \).
        \begin{enumerate}
            \item Monotonicity/Antitone: If \( X \leq Y\), then \(\rho(X) \geq \rho(Y) \).
            \item Cash invariance: If \( m \in \mathbb{R} \), then \( \rho(X + m) = \rho(X) - m \).
        \end{enumerate}
        It is called normalized if \( \rho(0) = 0 \), convex if \( \rho \) is a convex functional, and coherent if it is in addition positively homogenous,
        that is \( \rho(\lambda X) = \lambda \rho(X),\ \lambda \in \mathbb{R}_{\geq 0} \).
    \end{definition}
    \begin{remark}
    If we say risk measure, we mean monetary risk measure, if not otherwise stated. The concept of coherence could be referred to as a sublinear 
    risk measure in functional analytic terminology.
    \end{remark}
    \begin{definition}
        A risk measure \( \rho \) is
        \begin{enumerate}
            \item sensitive, if \( \rho(-X) > \rho(0) \) for \( X \in L^\infty_{+}(\Omega, \mathcal{F}, \mathbb{P}) \) and \( \pp{X > 0} > 0 \),
            \item law-invariant, if \( \rho(X) = \rho(Y) \) for \( X \sim Y\) under \( \mathbb{P} \),
            \item continuous from below, if \( X_n \nearrow X \implies \rho(X_n) \searrow \rho(X) \),
            \item continuous from above, if \( X_n \searrow X \implies \rho(X_n) \nearrow \rho(X) \).
        \end{enumerate}
    \end{definition}

    \begin{definition}[Linear cones]
    A set \( S \) in a real vector space \( \mathcal{X} \) is a cone if \( x \in S \implies \lambda x \in S \) for \( \lambda \in \mathbb{R}_{>0} \).
    \end{definition}
    \begin{remark}
       To differentiate cones as in the previous from the ones such as in Definition \ref{coneofrings}
       we call the first linear cones and the latter algebraic cones.
    \end{remark}
    \begin{definition}
        The acceptance set of a risk measure \( \rho \) is 
        \[ \mathcal{A}_\rho = \{ X \in \mathcal{X} | \rho(X) \leq 0 \}. \]
    \end{definition}
    \begin{proposition} \label{acceptancesetpropisriskprop}
        Assume \( \mathcal{A}_{\rho} \neq \emptyset \), it holds:
        \begin{enumerate}
            \item \( \rho(X) := \inf \{ m \in \mathbb{R} | m + X \in \mathcal{A}_{\rho} \}   \) 
            \item \( \rho \) is a convex risk measure if and only if \( \mathcal{A}_{\rho} \) is convex.
            \item \( \rho \) is positive homogenous if and only if \( \mathcal{A}_{\rho} \) is a cone.
            \item \( \rho \) is coherent if and only if \( \mathcal{A}_{\rho} \) is a convex cone 
        \end{enumerate}
    \end{proposition}
    \begin{proof}
        \cite{foellmerschied} Proposition 4.6
    \end{proof}
    %Foellmer \& Schied 
    
    One might suggest that the acceptance set \( \mathcal{A}_\rho \) could correspond to an algebraic cone (Definition \ref{coneofrings}) in the ring 
    \( L^p(\Omega, \mathcal{F}, \mathbb{P}) \) or even better an ideal. However, there are again strong obstructions to this:

    \begin{proposition} \label{acceptancesetisnotideal}
        The acceptance set \( \mathcal{A}_\rho \) of a subadditive, normalized risk measure \( \rho \) being an ideal is equivalent to 
        \( X \in \mathcal{A}_{\rho} \iff \rho(XY) \leq 0 \)
        for all \( Y \in L^p(\Omega, \mathcal{F}, \mathbb{P}) \).
    \end{proposition}
    \begin{proof}

\begin{enumerate}
    \item \( \Rightarrow \)
    \begin{itemize}
        \item By the definition of an ideal \( X \in \mathcal{A}_\rho \implies XY \in \mathcal{A}_\rho \) for all \( Y \in L^p(\Omega, \mathcal{F}, \mathbb{P}) \)
            and \( XY \in \mathcal{A}_\rho \iff \rho(XY) \leq 0 \).
    \end{itemize}
    \item \( \Leftarrow \)
    \begin{itemize}
        \item We have for \( X, Y \in \mathcal{A}_{\rho} \) that \( \rho(X), \rho(Y) \leq 0  \) and by subadditivity \( \rho(X + Y) \leq \rho(X) + \rho(Y) \),
            and due to the assumption the RHS is less than or equal to \( 0 \), so \( X + Y \in \mathcal{A}_{\rho} \). Since \( \rho \) is normalized we have
            that \( \rho(0) = 0 \leq 0 \) so \( 0 \in \mathcal{A}_{\rho} \). As \(L^p(\Omega, \mathcal{F}, \mathbb{P}) \) is a ring, 
            \( -1 \in L^p(\Omega, \mathcal{F}, \mathbb{P}) \) and the additive inverse of any \( X \in L^p(\Omega, \mathcal{F}, \mathbb{P}) \) is clearly
            \( -1 \cdot X \), therefore if \( X \in \mathcal{A}_{\rho} \), by hypothesis also \( - X \in \mathcal{A}_\rho \), so \( \mathcal{A}_\rho \) is an abelian group
            with respect to addition. The multiplicative property follows also by assumption.
    \end{itemize}
\end{enumerate}
\end{proof}
As risk measures are antitone and for any \( X \in \mathcal{A}_{\rho} \) will accept all \( Y \geq X \) in \( L^p(\Omega, \mathcal{F}, \mathbb{P}) \), 
the multiplicative absorption property of ideals is especially problematic. As the \( Y \) accepted become quite large (only bounded due to norm restrictions
of the \( L^p \)), we also accept every \( -Y \), a rather undesirable feature. In short, there is no such risk measure, whose \( \mathcal{A}_{\rho} \) 
is an ideal except a special case, for which we need to adjust our definition of risk measures to the extended real numbers (see also Remark \ref{completionofriskmeasures}, 
and is then the one, which accepts all of \( L^\infty(\Omega, \mathcal{F}, \mathbb{P}) \).


%TODO this "equivalence" is flaky, you need also to show that any acceptance set which is an algebraic cone induces 
\begin{proposition} \label{acceptanceisnotcone}
        The acceptance set \( \mathcal{A}_\rho \) of a normalized, subadditive risk measure \( \rho \) being an algebraic cone in \( L^p(\Omega, \mathcal{F}, \mathbb{P}) \) 
        is equivalent to 
        \( X \in \mathcal{A}_{\rho} \iff \rho(XY) \leq 0 \) for all \( Y \in \mathcal{A}_{\rho} \). For any such risk measure, \( \mathcal{A}_{\rho} \) is a proper alg. cone in 
        \( L^p(\Omega, \mathcal{F}, \mathbb{P}) \).
    \end{proposition}
    \begin{proof}
        Since algebraic cones add the condition \( X \in L^p(\Omega, \mathcal{F}, \mathbb{P}) \implies X^2 \in P \) to the properties of ideals
        and weaken the requirement of \( X \in \mathcal{A}_{\rho} \implies Y X \in \mathcal{A}_{\rho} \) only to \( Y \in \mathcal{A}_{\rho} \)
        instead of \( Y \in  L^p(\Omega, \mathcal{F}, \mathbb{P}) \),
        by Proposition \ref{acceptancesetisnotideal} it suffices to show that this condition holds for any risk measure. 
        Take any \( X \in L^p(\Omega, \mathcal{F}, \mathbb{P}) \) then \( X^2 \geq 0 \) and by the inverse monotonicity of the risk measure,
        \( \rho(X^2) \leq \rho(0) = 0 \), so \( X^2 \in \mathcal{A}_{\rho} \). Similarly \( 0 \geq -1 \), so \( 1 = \rho(-1) \geq \rho(0) = 0 \) and \( -1 \notin \mathcal{A}_{\rho} \).
    \end{proof}

    \begin{example}
       Consider the worst-case risk measure \( \rho(X) = \text{ess sup } (-X) = - \text{ess inf } X \),
       which is normalized and subadditive.
       Clearly any \( X \in \mathcal{A}_{\rho} \) satisfies \( X \geq 0 \) a.s., and for \( Y \in \mathcal{A}_{\rho} \)
       we have \( XY \geq 0 \) a.s., so \( XY \in \mathcal{A}_{\rho} \). By Propositions \ref{acceptanceisnotcone}
       \( \mathcal{A}_{\rho} \) is an algebraic cone, the algebraic cone of almost surely positive random variables.
       However, \( \mathcal{A}_{\rho } \) is not an ideal, because if \( X \in \mathcal{A}_{\rho} \) then \( -1 \cdot X \notin \mathcal{A}_{\rho } \).
    \end{example}
    More of such risk measures can easily be created if we choose as their acceptance sets linear cones contained in the cone of a.s. non-negative random variables,
    (e.g. \( \text{ess sup }_{\omega \in S} -X(\omega) \) for fixed \( S \subseteq \Omega \)), but this 
    makes the requirement of \( \mathcal{A}_{\rho} \) being an algebraic cone a rather strict one.
    The reason being the purely algebraic point view on \( L^p(\Omega, \mathcal{F}, \mathbb{P}) \). We don't
    include information about how \( \mathbb{P} \) affects the weight of some event for the random variables. While
    \( X(\omega) = \omega^2 \) is positive for \( \Omega = \mathbb{R} \) and \( \mathcal{F} = \mathcal{B}(\mathbb{R}) \) (the Borel algebra), 
    and \( Y(\omega) = \omega \) is only for \( \omega > 0 \), if \( \text{supp } \mathbb{P} = \mathbb{R}_{>0} \), there is no risk involved
    in the position \( Y \). This aspect is however invisible if seeing \( L^p(\Omega, \mathcal{F}, \mathbb{P}) \) 
    directly as something similar to \( \mathbb{R}[x_1, \dots, x_n] \).

    %, in particular diversification effects are not respected (diversification is usally expresed in terms of addition
    % but problems occur here only for multiplicative events, which don't have a real analogue in terms of portfolio holdings

    \begin{example}
        Consider the counterexample of the coherent risk measure \( \rho(X) = \mathbb{E}[-X] \), let \( X = 3 \cdot \mathbf{1}_{A} \) and \( Y = \mathbf{1}_{B} - \mathbf{1}_{A} \) 
        with \( A, B \in \mathcal{F} \) and \( \pp{B} > \pp{A} \neq 0 \) and \( B \cap A = \emptyset \), then \( \rho(X) = -3 \cdot \pp{A} < 0 \) and \( \rho(Y) = \pp{A} - \pp{B} < 0\),
        so both \( X,Y \) are acceptable. But \( \rho(XY) = 3 \cdot \pp{A} > 0 \), hence \( XY \notin \mathcal{A}_{\rho} \).
        In particular, this shows that even if \( \mathcal{A}_{\rho} \) is a linear cone it is not necessarily an algebraic one.
    \end{example}
    One could claim that products of random variables are something not considered in a risk management setting and typically risky positions are represented by 
    linear combinations with scalars. Against this stands however any kind of portfolio, which is subject to currency risks. For example if one is a pension insurer in Germany, 
    who owns a large quantity of US treasuries, whose value is denoted by \( X \), they not only face the credit risk of the US government, but also fluctuations in the USD/EUR exchange rate symbolized by \( R \). The model for the domestic value would then be of the form \( RX \).

    Fortunately, the situation is different, if we focus on random variables which are polynomials over an event space \( \Omega \), which is a real field or a subset thereof, 
    or specific risk measures, which are themselves polynomials or parameterized polynomial distributions.
    Indeed, the acceptance set already looks like the condition for some semi-algebraic set, which correspond to cones according to Example \ref{exampleconesinrings}.
    \begin{example} \label{accsetsemialgexample}
        Suppose \( \Omega \) is discrete and \( p_i = \mathbb{P}_{\theta}[X = x_i] \) polynomially parameterized with 
        \( \theta \in \Theta \) via \( p_i = g_i(\theta) \).
        Let \( \rho(X) = \mathbb{E}[-X] \) be the coherent expected value risk measure. Then the set of acceptable
        risks is 
        \[
            - \sum_{i} x_i g_i(\theta) \leq 0,
        \]
        which is semi-algebraic set. Note that we can leave the \( x_i \) undetermined for greater flexibility.
        The standard deviation risk measure is given by
        \( \rho(X) = - \left( \expv{X} + \alpha \sqrt{\text{Var}[X]} \right) \)
        the corresponding acceptance set is given by
        \[
            - \left( \sum_{i} x_i g_i(\theta) + \alpha\sqrt{\sum_{j} g_j(\theta)\left(x_j - \sum_{i} x_i g_i(\theta)\right)^2} \right) \ \leq 0
        \]
        which is not semi-algebraic. However, \( \alpha \sqrt{\var{X}} \geq 0 \) and \( \rho(X) \leq 0 \iff \expv{X} + \alpha \sqrt{\var{x}} \geq 0 \)
        which holds iff. \( \expv{X} \geq 0 \) or \( \expv{X} \leq 0 \) and \( |\expv{X}| \leq \alpha \sqrt{\var{X}} \iff \expv{X}^2 \leq \alpha^2 \var{X}  \), 
        which can be written as the union of two semi-algebraic sets
        \begin{align*} 
            - \sum_{j} g_j(\theta) x_j &\leq 0
        \end{align*} 
        and
        \begin{align*} 
            \sum_{j} g_j(\theta) x_j &\leq 0 \\
            (1 + \alpha^2) \left(\sum_{i} x_i g_i(\theta)\right)^2 - \alpha^2 \sum_{j} g_j(\theta) x_j^2  &\leq 0 
        \end{align*}
        An analogue of this also underlies the Markowitz portfolio optimization.
    \end{example}
    While for simple models or single-variate standard distributions, this realization doesn't deliver more insight (after all their moments in terms of standard parameterizations, 
    are well known), it can be a viable approach for mixtures or non-standard models/approximations.
    \iffalse

    \begin{theorem}
        Let \( g : [0, 1] \to [0, 1] \) be a monotone function with \( g(0) = 0, g(1) = 1 \). 
        The function \[ 
            c_g : \mathcal{F} \to [0, 1],\ A \mapsto  g(\mathbb{P}[A]),
        \]
        is referred to as the distortion of \( \mathbb{P} \) by \( g \) or short distortion.
        Any distortion is in the norm dual of \( L^\infty(\Omega, \mathcal{F}, \mathbb{P}) \)
        that is \( \text{ba}(\Omega, \mathcal{F}, \mathbb{P}) \).
    \end{theorem}
    \begin{proof}
        
    \end{proof}
    \begin{theorem}
        Let \( c_g : \mathcal{F} \to [0, 1] \) be a distortion then the integral
        for \( X \in \mathcal{X} \)
        \[
            \int X dc := \int_{-\infty}^0 (c(X > x) - 1) dx + \int_0^\infty c(X > x) dx
        \]
        is well defined and a positive linear functional. The integral on the RHS is 
        in the Riemann sense.
    \end{theorem}
    \begin{proof}
        This is a special case of Theorem 11.8 in \cite{infinitedimanalysis}.
    \end{proof}
    \begin{theorem}
        For a distortion \( c_g : \mathcal{F} \to [0, 1]\) define the functional
        \[
            \rho_g(X) = \int - X dc,
        \]
        then \( \rho(X) \) is a risk measure. The family of all such risk measures are called distortion risk measures.
    \end{theorem}
    \begin{proof}
        Refer to Section 2 of \cite{disentanglingdrm} for a broader introduction of this subject.
    \end{proof}
    \begin{corollary}
        The acceptance sets of distortion risk measures \( \rho_g \) are cones.
    \end{corollary}
    \begin{proof}
        Let \( X \in \mathcal{A}_{\rho_g} \) then for \( \lambda \geq 0 \)
        \begin{align*}
            \rho_g(X) &\leq 0 \\
            \int - X dc &\leq 0 \\
            \int - \lambda X dc &\leq 0 \\
            \rho_g(\lambda X) &\leq 0.
        \end{align*}
    \end{proof}
    \fi
    \end{subsection}
