\begin{section}{Algebraic Geometry}
\begin{subsection}{Varieties, Coordinate Rings and the Spectrum}
Algebraic Geometry started out with the fundamental question of finding the solutions to polynomial equations or statements.
Interpreting solution sets geometrically has more than aesthetical and intuitive value, but also opens the door to many
unexpected results and challenging problems such as resolving Fermat's last theorem.
Moreover the modern approach, which was set in motion by Alexander Grothendieck and his "Éléments de géométrie algébrique" (EGA) had  
not only a profound impact to this subfield, but changed the way, we practice mathematics as a whole. For example the axiomatic use 
of categories, the reinterpretation of logic via topoi and topology without points are due to him. 
%For our concrete applications we will mostly need classical algebraic geometry
%(that is analyzing solution sets of polynomials in analoga of \( \mathbb{K}^n \) and their corresponding coordinate rings). 

For the algebraic
version of the geometry of risk measures the modern approach is more viable (that is using general spectra of algebraic structures and categorical notions).
Of course we can cover only a small set of subjects of this vast field, so we assume the reader to know some algebra,
such as the theory of rings, ideals, morphisms and field theory, as well as some basic topology and functional analysis.
A little category theory also comes in handy, but not too much beyond the basic definitions. 
For a broader introduction, the author recommends Cox's et al. "Ideal, Varieties and Algorithms" \cite{cox2008ideals} and for those who feel also inclined
to a more abstract interpretation, Milne's "Algebraic Geometry" \cite{milne2012algebraic}.
\begin{definition}[Algebro-Geometric Objects] \label{affinealgeodefs}
    The central definitions are:
\begin{enumerate}
    \item The \( n \)-dimensional affine space over a field \( \mathbb{K} \) is \(\mathbb{A}^n_{\mathbb{K}} = \mathbb{K}^n\).
    \item The ring of polynomials in \( n \) variables over \( \mathbb{K} \) is \( \mathbb{K}[x_1, \ldots, x_n] \).
    \item Given an ideal \( I \subseteq \mathbb{K}[x_1, \ldots, x_n] \), the algebraic set defined by \( I \) is  
        \[ V(I) = \{\, a \in \mathbb{K}^n : f(a) = 0 \text{ for all } f \in I \,\} \]
    \item For \( S \subseteq \mathbb{K}^n \), its vanishing ideal is  
       \[
       I(S) = \{\, f \in \mathbb{K}[x_1, \ldots, x_n] : f(a) = 0 \text{ for all } a \in S \,\}
       \]
    \item An affine variety is a non-empty, algebraic set in \( \mathbb{A}^n_\mathbb{K} \).
    \item An algebraic set \( V \) is irreducible if it cannot be written as the union of two proper algebraic subsets.
   \item The quotient ring \( \frac{\mathbb{K}[x_1, \ldots, x_n]}{I(V)} \) for an irreducible affine variety is 
       also referred to as the coordinate ring \( \mathbb{K}[V] \).
   \item A function \( f : V \to \mathbb{K} \) is regular if \( f \in k[V] \).
   \item The ring of the following rational polynomials 
       \[ 
           \mathbb{K}(V) := \{ \frac{f}{g} | f, g \in \in \mathbb{K}[V] \text{ and } g \notin I(V) \} 
       \]
       is the function field on \( V \).
   \item One can construct the Zariski Topology on \(\mathbb{A}^n_\mathbb{K}\), where the closed sets in this topology on \( \mathbb{A}^n_k \) are the algebraic sets.
\end{enumerate}
\end{definition}
\begin{remark}
We are mainly interested in the cases \( \mathbb{K} = \mathbb{R} \) or \( \mathbb{K} = \mathbb{C}\).
Unless otherwise stated, the term "variety" will refer to affine irreducible varieties. One should be cautious how an author defines a variety, since there are different
restrictions which in some contexts simplify analysis and complicate it in others. There also different terminologies which sometimes mean the same such as 
algebraic spaces.
\end{remark}

\begin{example}
The simplest algebraic objects are arguably the whole space, represented by the ideal \(J_1 = (0)\), and the empty set, represented by a constant ideal \(J_2 = (c)\). 
Considering the affine space \(\mathbb{A}_\mathbb{K}\), the corresponding quotient rings are 
\[
\frac{\mathbb{K}[x_1]}{J_1} \simeq \mathbb{K}[x_1] \quad \text{and} \quad \frac{\mathbb{K}[x_1]}{J_2} \simeq 0,
\]
since \(\mathbb{K}\) is a field, so \( c \) is invertible. Indeed, if \(c c^{-1} = 1\) but \(c = 0\), then all scalars must vanish as well.

Next, consider points; for example, in \(\mathbb{A}^2_\mathbb{R}\), every \((c_1, c_2)\in \mathbb{R}^2\) corresponds to the ideal \(J = \langle x_1 - c_1, x_2 - c_2 \rangle\), 
so that \(V(J) = \{ (c_1, c_2) \}\). The quotient ring satisfies \(\frac{\mathbb{R}[x_1, x_2]}{J} \simeq \mathbb{R}\), since \(x_i - c_i = 0\) forces each polynomial 
to be evaluated at the point \((c_1, c_2)\). Note that every polynomial vanishing at \((c_1, c_2)\) is sent to \( 0 \). 
This motivates the construction of \(\mathbb{K}[V]\), which consists of all polynomial maps \(V \to \mathbb{K}\), and also identifies functions that are equivalent on \( V \); 
e.g., \(h(x_1, x_2) = 2\) and \(g(x_1, x_2) = 2 + (x_1 - c_1)(x_2 - c_2)\) agree on \( V \) .

It is interesting to note that the only prime or maximal ideal in this ring (in fact, a field) is \((0)\). A similar analysis applies to the line \(x_1 = x_2\) in \(\mathbb{C}^2\), 
cut out by the vanishing locus of \(f(x_1, x_2) = x_1 - x_2\). The quotient ring is 
\[
\frac{\mathbb{C}[x_1, x_2]}{\langle f \rangle} \simeq \mathbb{C}[x_1],
\]
whose nontrivial prime ideals are generated by points \((x_1 - c_1)\). Interestingly, one can pair each prime ideal \( (x_1 - c_1) \) to a point \( (c_1, c_2) \) on the variety 
specified by \(f(x_1, x_2) = 0\).
\end{example}

To direct the attention more to the prime ideal aspect of the previous example, 
we add a definition which is central in the modern treatment of algebraic geometry,
and matters to us, because we will need it to properly state the positive Nullstellensaetze.

\begin{definition}
   Let \( R \) be a commutative unital ring (as are all rings in this work).
   The set of all prime ideals in \( R \), is called the spectrum, denoted \( \spec{R} \).
\end{definition}

To do geometry in \( \spec{R} \) one requires some degree of understanding of how points are spaced to each other:
\begin{definition}
    There is a topology on \( \spec{R} \), the Zariski topology, whose basis of open sets,
    is given by \( D_f \subseteq \spec{R} \) with \( D_f = \{ \mathfrak{p} \in \text{Spec } R | f \notin \mathfrak{p} \} \) 
    for some \( f \in R \) (the \( D \) stands for domain). Conversely a basis of closed sets is given by
    \( V(E) = \{ \mathfrak{p} \in \spec{R} | \forall f \in E,  f \in \mathfrak{p} \} \), (\( V \) for vanishing set).
\end{definition}

While we have a topology a more concrete notion of distance couldn't come from the Zariski topology,
which satisfies the \( T_1 \)-separation axioms and fullfills quasicompactness for closed sets, but never Hausdorfness 
(except if \( \mathbb{K} \) is finite), 
so by the Nagata–Smirnov metrization theorem there can not be a metric. However, the Zariski topology is rather coarse,
and the finer Euclidean topology enables often a metric for subsets of varieties, which is at least continuous in the Zariski sense. 
Why is it sensible to consider points \( \mathfrak{p} \) in \( \spec{R} \) s.t. \( f \in \mathfrak{p} \) instead of
\( p \in \aff{\mathbb{K}}{n} \) s.t. \( f(p) = 0 \)? First one notices that in \( \mathbb{K}[X] / \mathfrak{p} \), 
the equivalence class of \( [f] \) is precisely \( [0] \) if \( f \in \mathfrak{p} \), secondly we have
Hilbert's weak Nullstellensatz.
\begin{theorem} \label{weakhilbertnull}
    If \( \mathbb{K} \) is an algebraically closed field, then the maximal ideals of \( \mathbb{K}[x_1, \dots, x_n] \)
    are precisely those ideals of the form \( \langle x_1 - p_1, \dots, x_n - p_n \rangle \), where \( p_i \in \mathbb{K} \).
\end{theorem}
As any maximal ideal is already prime, we see that \( V(f) \) already entails the points \( p \) such that \( f(p) = 0 \) as maximally ideals.
Moreover, it allows us to encode points which are not in \( \mathbb{K}^n \) via their minimal irreducible  polynomials, e.g.
if \( \aff{\mathbb{K}}{1} = \mathbb{R} \) and \( f(x) = x^4 - 1 \), then the roots in the algebraic closure are precisely \( \{1, -1, i, -i\} \),
but of course in \( \aff{\mathbb{R}}{1} \) there are only \( \{ 1, -1 \} \), however \( \mathfrak{p} = \langle x^2 + 1 \rangle \in \mathbb{R}[x] \) 
is prime and also \( f \in \mathfrak{p} \), so we retain some information about roots even if there are not available in the underlying field.


\begin{definition}[Local ring at \( \mathfrak{p} \)]
    The local ring at a point \( \mathfrak{p} \in \spec{R} \) is the localization \( R_{\mathfrak{p}} := S^{-1} R  \)
    with the multiplicative set \( S := R \setminus \mathfrak{p} \).
\end{definition}
There is a bijection \( \spec{ S^{-1} R } \leftrightarrow T \subset \spec{R} \), where \( T \) is the subset of prime ideals disjoint of \( S \).
For a multiplicative set \( S \) induced by a prime ideal \( \mathfrak{p} \) as above, it then follows that the ring \( R_{\mathfrak{p}} \)
has a unique maximal ideal which is the image of \( \mathfrak{p} \) under the map \( R \to R_{\mathfrak{p}} \).
Keep in mind that a homomorphism \( \phi : R_{\mathfrak{p}} \to A_{\mathfrak{q}} \) between local rings, means that 
\( \phi(\mathfrak{p}) = \mathfrak{q} \).

This unique maximal ideal allows to construct a field out of \( R_{\mathfrak{p}} \):
\begin{definition}[Residue field]
    The residue field \( \resf{\mathfrak{p}} \) at a point \( \mathfrak{p} \in \spec{R} \) is the quotient ring \( \frac{R_{\mathfrak{p}}}{\mathfrak{p}} \) of the local ring \( R_{\mathfrak{p}} \).
\end{definition}
This insight also affects the language involved, meaning geometers tend to express certain relations of functions on varieties in \( \aff{\mathbb{K}}{1} \) via their analogues in \( \spec{R} \). For example, a function \( f \in \mathbb{K}[V] \) vanishes at the point \( \mathfrak{p} \) 
if \( f \in \mathfrak{p} \) or equivalently \( [f] = 0 \) under the map \( \mathbb{K}[V] \to \resf{\mathfrak{p}} \), more broadly the "value" of \( f \)
at \( \mathfrak{p} \) refers to the image of \( f \) under \( \mathbb{K}[V] \to \resf{\mathfrak{p}} \). This convention is evident for the case
\( \mathbb{K} = \mathbb{C} \) and \( R = \mathbb{C}[X] \), since the spectrum coincides with the maximal spectrum 
\( \text{Specm } R \) (the set of maximal ideals), and by the Hilbert weak Nullstellensatz for any \( \mathfrak{p} \in \spec{R} \), 
\[ 
\resf{\mathfrak{p}} = \frac{(\mathbb{C}[X] \setminus \langle x_1 - p_1, \dots, x_n - p_n \rangle)^{-1}\mathbb{C}[X]}{\langle x_1 - p_1, \dots, x_n - p_n \rangle} \]
therefore each \( f \in R \) is sent to \( f(p_1, \dots, p_n) \), which is the same as the classical notion of the value of a function.

In fact all inspection of varieties and solution sets to polynomial equations can be purely done on \( \spec{R} \), which has many benefits 
of handling certain phenomena better and is less "forgetful" about certain properties of the vanishing sets and can even be transfered to objects,
which might not appear to be algebraic sets initially. Though, one requires a bit more construction to do so properly. 
%a collection of mappings \( \mathcal{O} \to \textbf{Set} \), 
% for all open \( U, V \subseteq X \), there is a map  s.t. \( V \subseteq U \), 
\begin{definition}[Presheaves and Sheaves]
    Given a topological space \( X \), a sheaf is a structure s.t. 
    for all open \( U \subseteq X \), there is a map of sets \( \mathcal{O} : U \to \mathcal{O}(U) \) 
    and for all open \( V \subseteq U \) with their respective inclusion \( \iota : V \to U  \),
    corresponds a map \( r_{U,V} : \mathcal{O}(U) \to \mathcal{O}(V) \).
    The \( r \) stands for restriction and we use the notation \( f|_V := r_{U, V}(f) \) for \( f \in \mathcal{O}(U) \). Additionally 
    the maps should satisfy:
    \begin{enumerate}
        \item \( r_{U, U} = \text{id}_{\mathcal{O}(U)} \)
        \item If \( U \subseteq W \) then \( r_{U, V} \circ r_{W, U} = r_{W, V} \).
        \item (Locality): For a cover \( \bigcup_i U_i = U \) and  \( f, g \in \mathcal{O}(U) \), s.t. \( f|_{U_i} = g|_{U_i} \) 
            for all \( i \), then \( f = g \).
        \item (Gluing): For a cover \( \bigcup_i U_i = U \) and a collection \( \{ f_i \}_i,\ f_i \in \mathcal{O}(U_i) \), 
           s.t. \( f_i|_{U_i \cap U_j} = f_j|_{U_i \cap U_j} \), then there exists \( f \in \mathcal{O}(U) \)
           s.t. \( f|_{U_i} = f_i \).
    \end{enumerate}
    A structure which only satisfies the first two properties is a presheaf. If it also satisfies locality it is separated.
\end{definition} 
The quite general definition hints already at the fact that sheaves are ubiquitous in mathematics, e.g. smooth functions over a manifold
form a sheaf, the sheaf of Schwartz distributions over a space and there is even a sheaf of measures on Borel spaces \cite{sheafmeasures}.
In the affine case here, there is a particular choice of sheaf, which got its own name. For this we also need to define morphisms.
\begin{definition}[Morphism of sheaves] \label{sheafmorphism}
    A morphism \(\varphi : \mathcal{F} \to \mathcal{G}\) of sheaves on \(X\) is a rule which assigns to each open \(U \subseteq X\) 
    a map of sets \(\varphi : \mathcal{F}(U) \to \mathcal{G}(U)\) compatible with restriction maps, i.e., whenever \(V \subseteq U \subseteq X\) are open 
    the following diagram commutes: 
    \[
        \begin{tikzcd}
            \mathcal{F}(U) \arrow[r, "\varphi"] \arrow[d, "r_{U,V}"] & \mathcal{G}(U) \arrow[d, "r_{U,V}"] \\
            \mathcal{F}(V) \arrow[r, "\varphi"] & \mathcal{G}(V)
        \end{tikzcd}
    \]
    An isomorphism of sheaves is a morphism \( \varphi : \mathcal{F} \to \mathcal{G} \), s.t there exists a morphism 
    \( \varphi^{-1} : \mathcal{G} \to \mathcal{F} \), satisfying 
    \begin{align*}
        \varphi^{-1} \circ \varphi &= \text{id}_{(X, \mathcal{F})} \\
    \varphi \circ \varphi^{-1} &= \text{id}_{(Y, \mathcal{G})} 
    \end{align*}
\end{definition}
Note that if there exists a homeomorphism \( \pi : X \to Y \) between topological spaces, we can
also define morphisms of sheaves with different underlying spaces, namely if \( (X, \mathcal{F}) \) and \( (Y, \mathcal{G}) \)
are sheaves, then for a open sets \( U \subseteq X, V \subseteq Y \) then one could construct maps 
\( \varphi : \mathcal{F}(U) \to \mathcal{G}(\pi(U)) \), \( \varphi' : \mathcal{F}(\pi^{-1}(V)) \to \mathcal{G}(V)  \)
and if for all \( U \) (respectively \( V \)) these maps satisfy the definition of \ref{sheafmorphism},
we get a morphism between sheaves with different underlying space. Unfortunately, these can't be the same
(simply because \( X \) and \( Y \) are not the same space), but there's a one to one correspondence
(due the adjointness of the preimage sheaf and pushfoward sheaf functor). In case that \( \pi \)
is just a continuous map, one refers typically to morphisms of sheaves to the direction \( \varphi' : \mathcal{F}(\pi^{-1}(V)) \to \mathcal{G}(V) \) 
(so it is a morphism of sheaves on \( Y \)).

\begin{definition} \label{basisstructsheaf}
    Define for each basic open set \( D_f \subset \spec{R} \), where \( f \in R \)
    the map \( \mathcal{O}_{\spec{R}}(D_f) = R_f \), where \( R_f := S^{-1}R \) is the localization 
    of \( R \) with the multiplicative set \( S = \{f, f^2, f^3, \dots \} \) and the if \( D_g \subset D_f \)
    we use as the restriction \( r_{D_f, D_g}  \) the canonical map \( R_f \to R_g \).
    We call this the basis of the structure sheaf of \( \spec{R} \).
\end{definition}

\begin{theorem}[Affine scheme] \label{affinescheme}
    The basis of Definition \ref{basisstructsheaf} can be extended to all open subsets of \( \spec{R} \)
    and is called the structure sheaf 
    \[ 
        (\mathcal{O}_{\spec{R}}, \spec{R}) 
    \]
    or the affine scheme of \( R \).
\end{theorem}
\begin{proof}
    %The construction requires the use of stalks and projective limits, which are beyond the scope of standard algebra courses, so
    The interested reader is referred to Theorem 6.3 of \cite{boschag}.
\end{proof}

\begin{definition}[General Schemes] \label{defscheme}
    A sheaf \( (X, \mathcal{O}_X) \) s.t. for each \( x \in X \), there's an open set \( U \),
    s.t. there exists an isomorphism of sheaves \( \varphi : (U, \mathcal{O}_X(U)) \to (R_U, \mathcal{O}_{\spec{R_U}}) \)
    for rings \( R_U \) is called a scheme.
\end{definition}

In particular when the \( R_U \) are of the shape \( \mathbb{K}[X] / I \) for some ideal 
\( I = \langle f_1, \dots, f_n \rangle \) generated by polynomials \( f \in \mathbb{K}[X] \) we obtain not only a variety, but always a scheme too.
Later on, we will need so called stalks. The definition won't be used in the next sections, so we prefer to just state what it breaks down to for schemes. 
\begin{example}
    For an affine scheme, the stalk \( \mathcal{O}_{\spec{R}, \mathfrak{p}} \) at a point \( \mathfrak{p} \in \spec{R} \) is the local ring \( R_{\mathfrak{p}} \) at \( \mathfrak{p} \).
\end{example}
%\input{reg_morph}
\end{subsection}
\end{section}
